Assignment 1
Your first commit: hello_world.Rmd

For your first assignment, I want you to create a file called 01-assignment_<lastname>.Rmd
in your github repo in the assignments folder. It should contain the following
elements:

A sentence that says "Hello, World"

```{r}
"Hello, World"
```


R output that summarizes one of the variables in the colllege.Rdata
dataset
##Have to update packages and load data first.

install.packages("tidyverse")

```{r scorecard} 
rm(list=ls())
library(tidyverse)
```

## Load in the data
load("C:/Users/rayjm2/Desktop/Scripts/college.Rdata")

##Now we can create R output that summarizes one of the variables in the colllege.Rdata

Data for grab just the data for Vanderbilt, then look only at the average test scores and admit rate. 
I want to see the admission rate at Boston College.

```{r filter}
sc%>%filter(instnm=="Boston College")

sc%>%filter(instnm=="Boston College")%>%select(instnm, adm_rate)


##If you have extra time, you can do the following:
##Calculate the average earnings for individuals at the most selective colleges,
##then compare that with individuals at the least selective colleges in the
##dataset.

Find a way to determine whether colleges with very high SAT scores tend
to be larger or smaller than colleges with low SAT scores.

sc%>%filter(sat_avg<1200)%>%select(instnm, adm_rate)
sc%>%filter(sat_avg<1200)%>%select(instnm, adm_rate)

Plot the relationship between cost and debt. What do you see? Does this
surprise you?

##I tried multiple times to create a plot, but I kept getting an error for costt4_a not found
plot(costt4_a, debt_mdn, xlab="costt4_a", ylab=debt_m, pch=100)
    
Now, provide separate plots for cost and debt by control of the institution.