---
output:
  word_document: default
  html_document: default
---
##Assignment 3
##Jennifer Ray

##Use the attrition dataset to answer the following questions. 
##As always, your assignment must be turned in as a .Rmd file.

```{r  include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(forcats)
library(RColorBrewer)
library(knitr)
```

## Loading Data 
```{r}
load("C:/Users/rayjm2/Desktop/Scripts/week3_cnd/attrition.Rdata")
```


```{r}

at<-at%>%mutate(attrit=ifelse(Attrition=="Yes",1,0))

table(at$Attrition)

table(at$attrit)

table(at$attrit,at$Attrition)
```

##Create a graph that shows the distribution of monthly income.
```{r}
gg<-ggplot(at,aes(x=Department,fill=MonthlyIncome))
gg<-gg+geom_bar()
gg
``` 



##Create a graph that shows the average level of monthly income by field of education.

```{r}
## Summarize attrition by monthly income AND field of education
at_sum<-at%>%
  group_by(MonthlyIncome,EducationField)%>%
  summarize(attr_avg=mean(attrit))

## Get the results
at_sum
```

```{r}
## PLot it using a bar plot
gg<-ggplot(at_sum,aes(x=fct_reorder(EducationField,attr_avg),y=attr_avg,color=MonthlyIncome))
gg<-gg+geom_bar(stat="identity",aes(fill=MonthlyIncome),position="dodge")
gg<-gg+ylab("Pr(Attrition)")+xlab("EducationField")
gg
```



##Create another graph that shows average level of monthly income by field of education and gender.

```{r}

at_sum<-at%>%
  group_by(MonthlyIncome,EducationField,Gender)%>%
  summarize(attr_avg=mean(attrit))%>%
  arrange(-attr_avg)

at_sum
```

##Create a graph that shows average levels of monthly income by field of education, gender and job level (scale of 1-5, highest ranked employees are 5)     

```{r}
at_sum<-at%>%
  group_by(MonthlyIncome,EducationField,Gender,JobLevel)%>%
  summarize(attr_avg=mean(attrit))%>%
  ungroup()%>%
  arrange(attr_avg)

at_sum

gg<-ggplot(at_sum,aes(x=fct_reorder(MonthlyIncome,attr_avg),y=attr_avg))
gg<-gg+geom_bar(stat="identity",aes(fill=Gender),position="dodge")
gg<-gg+facet_wrap(~EducationField+JobLevel,ncol=5)

gg<-gg+ylab("Proportion of Employees Who Departed")+xlab("Category")
gg<-gg+theme(axis.text.x = element_text(angle = 50, hjust = 1))
gg<-gg+ggtitle("Departure by Education Field and Job Level")


```
