---
output:
  word_document: default
  html_document: default
---
##Assignment 4
##Jennifer Ray

##For this assignment, you'll need to open up, clean and save the following datasets, using the tools we've gone over in class. For each dataset, make sure that when you're done you have a nice, neatly labeled dataset that would be easy for you or another analyst to open and analyze. Save the result in an RData file using the names provided. You need to turn in an R script named 04-assignment_<lastname>.Rmd that cleanly creates all of the datasets requested (lower case only for your last name, please).


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r} 
library(tidyverse)
library(haven)
library(readxl)
```

##1. Panel data for OECD countries. Save as file name oecd.RData http://www.wiley.com/legacy/wileychi/baltagi/supp/Gasoline.dat

```{r} 

oecd<-read.table("C:/Users/rayjm2/Desktop/Scripts/Wk4 HW Data/oecd.rData")

```


##2. U.S. National Election Survey data from 2004. Save as file name nes.RData. http://www.uta.edu/faculty/story/DataSets.htm

```{r} 

nes<-read_sav("C:/Users/rayjm2/Desktop/Scripts/Wk4 HW Data/NES2004-3.sav")

```

##3. General social survey, student version. Save as file name gss.Rdata. http://www.uta.edu/faculty/story/DataSets.htm

```{r}
gss<-read_excel("C:/Users/rayjm2/Desktop/Scripts/Wk4 HW Data/gss.xls",skip=0,col_names = TRUE)

save(gss,file="gss.Rdata")

```

##4. Replication file for "STATISTICAL DISCRIMINATION OR PREJUDICE? A LARGE SAMPLE FIELD EXPERIMENT". Open up and save the mainData.csv file. Save it as maindata.RData. Available here, look under the "Data and Analysis" tab.


```{r}
mainData<-read_csv("C:/Users/rayjm2/Desktop/Scripts/Wk4 HW Data/mainData.csv.txt")
write_csv(mainData,path="mainData.csv")              

save(mainData,file="mainData.Rdata")

```



##5. The Lalonde dataset, covering work experiences in the Panel Study of Income Dynamics (psid). Save as psid.RData http://users.nber.org/~rdehejia/data/psid_controls.txt You'll find a description of the data that you'll need here.


```{r}

my.widths=c(1,#treated
            2, #age
            1, #race
            1, #ses
            1, #schtyp
            1, #prog
            2, #read
            2, #write
            2, #math 
            2, #science
            2 #socst
            )
            
my_positions<-fwf_widths(my.widths)


paid<-read_fwf("http://users.nber.org/
~rdehejia/data/psid_controls.txt",
                col_positions = my_positions)

              

save(paid,file="paid.Rdata")

```

