---
output:
  word_document: default
  html_document: default
---
##Assignment 5
##Jennifer Ray

```{r,echo=FALSE}
rm(list=ls())
library(tidyverse)
library(forcats)
library(ModelMetrics)
library(modelr)
```


##In this assignment, you'll be asked to predict reading scores using the ELS data.

##1. Create a regression that predicts reading scores as a function of SES, using the training data.

$$Y=\beta_0+\beta_1 x_1 +\beta_2 x_2+ ... \beta_k x_k + \epsilon$$
  
```{r}
load("els.RData")
```

```{r}
els%>%summarize(mean(bynels2m,na.rm=TRUE))

gg<-ggplot(els,aes(x=bynels2m))
gg<-gg+geom_histogram()
gg
```

```{r}
gg<-ggplot(els,aes(x=bynels2m))
gg<-gg+geom_density()
gg
```
```{r}

#Model 1: simple bivariate regression

mod1<-lm(bynels2m~byses1,data=els) #outcome on left, predictor on right 

summary(mod1)
confint(mod1)

g1<-ggplot(els, aes(x=byses1,y=bynels2m))+ #specify data and x and y
           geom_point(shape=1)+ #specify points
           geom_smooth(method=lm) #ask for lm line
g1

els<-els%>%add_predictions(mod1)%>%rename(pred1=pred) #predict using data in memory
 
## RMSE
rmse_1<-modelr::rmse(mod1,els);rmse_1

```



##2. Report the RMSE from a validation of your model using the testing data.
##RMSE = 12.272

##3. Add another covariate to your model from 1.
```{r}
#Part 2: Multiple regression

mod2<-lm(bynels2m~as.factor(bypared_nohs)+
           byses1,
          data=els)

summary(mod2) 

els<-els%>%add_predictions(mod2)%>%rename(pred2=pred)

rmse_2<-modelr::rmse(mod2,els); rmse_2

```

##4. Again report the RMSE from a validation of your model using the testing data. Did you model improve? By how much?
 ##RMSE = 12.275
 ## This did not improve much... only by 0.003
 