---
output:
  word_document: default
  html_document: default
---

##Assignment 6
##Jennifer Ray
##Complete the following steps using the .Rdata or file. I want you to use the ggplot library and commands for all plots. Use the els data to complete the following steps.



## Setup
##The code for today starts with the normal set of preliminaries, opening up the `els.RData` dataset and creating a codebook. 

```{r,echo=FALSE}

library(tidyverse)
library(forcats)
library(modelr)

load("els.RData")

```


##1. Choose a dependent variable and plot that dependent variable as a function of a continuous independent variable.  

##so, the dependent variable is the Math Scores
##and the independent variable is SES

```{r}
#Plot SES and math scores
g1<-ggplot(data=els,
           aes(x=byses1,y=bynels2m)
           )

g1<-g1+geom_point(alpha=.5,size=.25) # Add points at x and y
g1
```
##2. If you need to, adjust the scale of either the dependent variable or independent variable to make more sense.

```{r}

els_sum<-els%>%
  mutate(math_rank=percent_rank(bynels2m)*100)%>%
  mutate(math_rank_r=round(math_rank))%>%
  group_by(math_rank_r)%>%
  summarize(test_mean=mean(bynels2m,na.omit=TRUE))

g1a<-ggplot(els_sum,aes(x=math_rank_r,y=test_mean))

g1a<-g1a+geom_point()

g1a<-g1a+ylab("Test Scores")+xlab("Math Rank")

g1a

```

##3. Add a line of best fit to your graphic.

```{r}
g1b<-g1a+geom_smooth(method="lm") # Add a line
g1b
```

##4. Clean up the labeling and description of the graphic so that it could be presented to a broader audience.

```{r}
g1<-g1+geom_smooth(method="lm")
g1<-g1+geom_smooth(method = "loess",color="red")
g1<-g1+geom_smooth(color="orange")
g1<-g1+ylab("Socio Economic Status")+xlab("Math Test Scores")
g1
```




##5. In your .Rmd file, include a few sentences describing what the graphic above shows.

##It would appear that the higher Socio Economic Status impacts the improved Math Test Scores.

