---
output:
  word_document: default
  html_document: default
---
##Assignment 7
##For this assignment, I want you to use the Census ACS API to download and plot data. Complete the following steps:

##Libraries

```{r}
library(tidyverse)
library(rvest)
library(acs)
library(lubridate)
library(noncensus)
library(tigris)
```

##Loading Data for Sumner County TN
```{r}
## Look up fips code for county
lookup_code("TN","Sumner") 

state_fips<-"47"
county_stub<-"165"
```

##1. Download data for all of the zip codes in Sumner County on education levels.


```{r}
county_fips<-paste0(state_fips,county_stub)
```

```{r}
# Get dataset that matches all zip codes to cities, counties and states. 
county_to_zip<-read_csv("http://www2.census.gov/geo/docs/maps-data/data/rel/zcta_county_rel_10.txt")
save(county_to_zip,file="county_to_zip.Rdata")

#easier names to work with
names(county_to_zip)<-tolower(names(county_to_zip))

#Just zip codes in selected county
county_to_zip<-county_to_zip%>%
  filter(state==as.numeric(state_fips),county==county_stub)%>%
  select(zcta5,state,county)

#list of zip codes
ziplist<-county_to_zip$zcta5

#City names
data(zip_codes)

city_zip<-zip_codes%>%filter(zip%in%ziplist)%>%select(zip,city)

#Arrange in order
city_zip<-city_zip%>%arrange(as.numeric(zip))
```

The first step is to get the table from ACS. Below, I submit a request using my key to get table B15002, which contains information on education levels. 

```{r}
# Get your own key and save as my_acs_key.txt
acs_key<-"fb0a4712449f8e3fe101f353099541878aded7e8"
#List of tables: https://www.census.gov/programs-surveys/acs/technical-documentation/summary-file-documentation.html under, 1-year appendices
# b15002: education of pop over 25, by sex 
# b19001: household income over last 12 months

api.key.install(acs_key, file = "key.rda")

select_zip<-geo.make(zip.code=ziplist)

county_educ=acs.fetch(geography=select_zip,
                      endyear=2016,
                      table.number="B15002",
                      col.names="pretty",verbose=T)
#save(county_educ,file="county_educ_la.Rdata")  # <---- this may take a long time :(
acs.colnames(county_educ)
```



##2. Compute the proportion of the population that has a bachelor's degree or above by zip code.

```{r}
## Proprtion of individuals at college or above=
## number with college degree/
## total number
prop_coll_above<-divide.acs(numerator=(county_educ[,15]+
                                      county_educ[,16]+
                                      county_educ[,17]+
                                      county_educ[,18]+
                                      county_educ[,32]+
                                      county_educ[,33]+
                                      county_educ[,34]+
                                      county_educ[,35]),
                            denominator=county_educ[,1]
)### Double check -- are these the correct columns??!??

#prop with educational attainment=number with level of ed attain/total pop
```




##3. Download data for all of the zip codes in Sumner county on family income by zip code.

## Family Income Data
```{r}

# 19001-- family income           
county_income<-acs.fetch(geography=select_zip, 
                        endyear = 2016,
                        table.number="B19001", 
                        col.names="pretty")

acs.colnames(county_income)


```


##4. Compute the proportion of the population that has family income above 75,000.

```{r}
#Proportion above 75k-- 
prop_above_75<-divide.acs(numerator=(county_income[,13]+
                            county_income[,14]+
                            county_income[,15]+
                            county_income[,16]+
                            county_income[,17]),
                          denominator=county_income[,1]
                          )

                          
# Convert to tibble
county_df<-tibble(substr(geography(county_educ)[[1]],7,11),
                       as.numeric(estimate(prop_coll_above)),
                       as.numeric(estimate(prop_above_75))
)


# Give it easy to use names
names(county_df)<-c("zip","college_educ","income_75")
save(county_df,file="dav.RData")

head(county_df)

```


##5.Plot the proportion of residents with incomes above 75,000 as a function of income.


```{r}

gg<-ggplot(county_df,aes(x=college_educ,y=income_75))
gg<-gg+geom_point()
gg

```





