---
output:
  word_document: default
  html_document: default
  pdf_document: default
---
##Assignment 10 building on Assignment 5
##Jennifer Ray

```{r,echo=FALSE}
rm(list=ls())
library(tidyverse)
library(forcats)
library(ModelMetrics)
library(modelr)
```


##In this assignment, you'll be asked to predict reading scores using the ELS data.

##1. Create a regression that predicts reading scores as a function of SES, using the training data.

$$Y=\beta_0+\beta_1 x_1 +\beta_2 x_2+ ... \beta_k x_k + \epsilon$$
  
```{r}
load("C:/Users/rayjm2/Desktop/Scripts/Week 5/els.Rdata")
```

```{r}
els%>%summarize(mean(bynels2m,na.rm=TRUE))

gg<-ggplot(els,aes(x=bynels2r))
gg<-gg+geom_histogram()
gg
```

```{r}
gg<-ggplot(els,aes(x=bynels2r))
gg<-gg+geom_density()
gg
```
```{r}

#Model 1: simple bivariate regression

mod1<-lm(bynels2r~byses1,data=els) #outcome on left, predictor on right 

summary(mod1)
confint(mod1)

g1<-ggplot(els, aes(x=byses1,y=bynels2r))+ #specify data and x and y
           geom_point(shape=1)+ #specify points
           geom_smooth(method=lm) #ask for lm line
g1

els<-els%>%add_predictions(mod1)%>%rename(pred1=pred) #predict using data in memory
 
## RMSE
rmse_1<-modelr::rmse(mod1,els);rmse_1

```



##2. Report the RMSE from a validation of your model using the testing data.
##RMSE = 8.55

##3. Add another covariate to your model from 1.
```{r}
#Part 2: Multiple regression

mod2<-lm(bynels2r~as.factor(bypared_nohs)+
           byses1,
          data=els)

summary(mod2) 

els<-els%>%add_predictions(mod2)%>%rename(pred2=pred)

rmse_2<-modelr::rmse(mod2,els); rmse_2

```

##4. Again report the RMSE from a validation of your model using the testing data. Did you model improve? By how much?
 ##RMSE = 8.55
 ## This did not improve much... only by 0.01
 ## This is not a comparable predictor
 
 
##Assignment 10
##Based on your work in assignment 5, do the following:
##1. Create a 10-fold cross validation of your linear model predicting reading scores as a function of at least two covariates. Provide a summary table or graphic of the RMSEs from this cross validation.


```{r}
els_cf<-els%>%
  crossv_kfold(20)
els_cf
```

```{r}
rmse_mod1<-els_cf %>% 
  mutate(train = map(train, as_tibble)) %>% ## Convert to tibbles
  mutate(model = map(train, ~ lm(mod1,
                                 data = .))) %>%
  mutate(rmse = map2_dbl(model, test, rmse)) %>% ## apply model, get rmse
  select(.id, rmse) ## pull just id and rmse 
```
```{r}
summary(rmse_mod1$rmse)

gg<-ggplot(rmse_mod1,aes(rmse))
gg<-gg+geom_density()
gg
```



##2. Using a random partition, create 100 separate cross validations of your linear model predicting reading scores as a function of at least two covariates.

```{r}
els_cv<-els%>%
  crossv_mc(n=100,test=.2)
els_cv
```
##Provide a summary table or graphic of the RMSEs from this cross validation.
 
```{r}
mod1_rmse_cv<-els_cv %>% 
  mutate(train = map(train, as_tibble)) %>% ## Convert to tibbles
  mutate(model = map(train, ~ lm(mod1, data = .)))%>%
  mutate(rmse = map2_dbl(model, test, rmse))%>% 
  select(.id, rmse) ## pull just id and rmse 

mod1_rmse_cv
``` 
 
 
```{r}
summary(mod1_rmse_cv$rmse)

gg<-ggplot(mod1_rmse_cv,aes(rmse))
gg<-gg+geom_density(bins=50,fill="blue",alpha=.2)
gg

```



```{r}

## Define the model
mod2_formula<-formula("home_rank ~ 
                      coll_grad_pc + 
                      per_capita_inc+
                      homeown_rate+
                      median_hh_inc")


mod2_rmse_cv<-els_cv %>% 
  mutate(train = map(train, as_tibble)) %>% ## Convert to tibbles
  mutate(model = map(train, ~ lm(mod2, data = .)))%>%
  mutate(rmse = map2_dbl(model, test, rmse))%>% 
  select(.id, rmse) ## pull just id and rmse 

summary(mod2_rmse_cv$rmse)
summary(mod1_rmse_cv$rmse)

gg<-ggplot(mod2_rmse_cv,aes(x=rmse))
gg<-gg+geom_density(fill="orange",alpha=.2)
gg<-gg+geom_density(data=mod1_rmse_cv,aes(x=rmse),fill="blue",alpha=.2)
gg

```
