---
title: "Assignment 13"
author: "Jennifer Ray"
date: "August 1, 2019"
output:
  html_document:
    df_print: paged
---


```{r}
library(tidyverse)
library(plotly)
library(shiny)
library(leaflet)
library(tigris)
library(htmlwidgets)
```

## Intro

Interactive graphics can give your audience a lot of information directly at their fingertips. We'll go through three diferent types of interactive graphics. 

- Univariate Graphics
- Multivariate Graphics
- Mapping

```{r}
load("pd.Rdata")
```

## 1. Using the county dataset, create an interactive scatterplot of homeowner-ship by education levels.

```{r}
gg<-ggplot(pd,aes(x=coll_grad_pc,y=homeown_rate,size=pop2010,
                          text=paste0(county,
                           "<br>",
                           "Percent College Grad: ",
                           round(coll_grad_pc,1),
                           "<br>",
                           "HomeOwnership Rate: ",
                           prettyNum(homeown_rate,big.mark=",")
                           )))

gg<-gg+geom_point(alpha=.5,color="lightblue")

gg<-gg+xlab("Percent College Graduates")+ylab("Home Ownership Rate")

ggplotly(gg)


```


## 2. Again using the county dataset, follow the steps used in class to create an interactive map of homeownership by county in your home state.

```{r}
##counties shapefile
if(file.exists("cs.RData")==FALSE){
cs<-counties(year=2010)
save(cs,file="cs.RData")
}else{
  load("cs.Rdata")
}
```

```{r}
data(fips_codes)

## Specify the state you want to work with here
states_list<-c("TN")

## Filter fips code to get just those states
fips_codes<-fips_codes%>%group_by(state)%>%summarize(fips_code=first(state_code))
fips_list<-fips_codes%>%filter(state%in%states_list)
fips_list<-fips_list$fips_code
```

```{r}

## Switch names to lower case
names(cs)<-tolower(names(cs))

## subset to state list
cs<-cs[cs$statefp%in%c(fips_list), ]## Just states we want

##subset county dataset to be just college grads and county name
pd_sub<-pd%>%select(fips,coll_grad_pc,homeown_rate,county)%>%filter(grepl(states_list,county))

## Join the two datasets
cs<-geo_join(cs,pd_sub,"geoid10","fips")
```

```{r}
pal<-colorNumeric(
  palette="YlGnBu",
  domain=cs$coll_grad_pc
)
```

```{r}
popup<-paste0(cs$county,
              "<br>",
              "Percent College Graduates= ",
              cs$coll_grad_pc,
              "<br",
              "Home Ownership Rate= ",
              prettyNum(cs$homeown_rate,big.mark=",")
)
```

```{r}
map<-leaflet()%>%
  addProviderTiles("CartoDB.Positron")%>%
  addPolygons(data=cs,
              fillColor=~pal(coll_grad_pc),
              color="#b2aeae",
              fillOpacity = .7,
              weight=1,
              smoothFactor = .2,
              popup=popup
              )%>%
  addLegend(pal=pal,
            values=cs$coll_grad_pc,
            position="bottomright",
            title="Percent College Graduates",
            labFormat=labelFormat(suffix="%"))
                
  map
```






