---
title: "Assignment 11"
author: "Jennifer Ray"
output: word_document
---


##Assignment 11

##Complete the following steps:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##1. Using the nyclfights13 library, open all of the data tables and turn them into a database. Make sure to include flights, airlines, airports, weather and planes.

##Load the libraries...

```{r}
# Mostly taken from : http://cran.r-project.org/web/packages/dplyr/vignettes/databases.html circa 2014

#Get libraries
library(tidyverse)
library(nycflights13)
library(RSQLite)
library(pander)
```

##Open the tables...

```{r}
# Data sources from NYC flights
data(flights)
data(airlines)
data(airports)
data(weather)
data(planes)
```

##Format into databases...

```{r}
con <- dbConnect(RSQLite::SQLite(), ":memory:")

#Write flights tables to database (you won't usually do this)
dbWriteTable(con,
             "flights", 
             as.data.frame(flights))

dbWriteTable(con,
             "planes", 
             as.data.frame(planes))

dbWriteTable(con,
             "airlines", 
             as.data.frame(airlines))

dbWriteTable(con,
             "weather", 
             as.data.frame(weather))

dbWriteTable(con,
             "airports", 
             as.data.frame(airports))
```

##Check which tables we have access to:

```{r}
#List tables in database
dbListTables(con)
```

##Check what fields are included...

```{r}
#List fields in various tables
dbListFields(con,"airlines")

dbListFields(con,"flights")

dbListFields(con,"planes")

dbListFields(con,"weather")

dbListFields(con,"airports")

```

##2. Create a data frame from a SQL pull from the database that consists only of flights that took off from JFK in May.


```{r}
#Generate a SQL request to a database
flight_text<-"SELECT f.month, f.origin, f.flight
              FROM flights f
              WHERE f.month=5 AND f.origin='JFK'"
flight_req<-dbSendQuery(con,flight_text)
flight_df<-dbFetch(flight_req,n=-1)
dbClearResult(flight_req)
head(flight_df)

```



# Question 3:  

##Create a data frame from a SQL pull from the database that consists only of flights that took off on-time (a delay of less than 10 minutes) from Newark at temperatures of less than 40 degrees F.

```{r}
#SQL request, flight info combined with weather info
weather_text<-"SELECT f.dep_delay, f.origin, w.temp, f.flight
              FROM weather w
              JOIN flights f 
              ON f.year=w.year
              AND f.month=w.month
              AND f.day=w.day
              WHERE f.dep_delay<10 AND f.origin='EWR' AND w.temp<40"
weather_req<-dbSendQuery(con,weather_text)
weather_df<-dbFetch(weather_req,n=-1)
dbClearResult(weather_req)
head(weather_df)
```




##4. Create data frame from a SQL pull from the database that consists of planes flown by United.

```{r}
#New request: which carriers have longer delays? 
united_text<-"SELECT f.flight, f.carrier 
            FROM flights f 
            WHERE f.carrier='UA'"
            
united<-dbSendQuery(con,united_text)
united_df<-dbFetch(united,n=-1)
dbClearResult(united)
head(united_df)
```



